Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-06 wsdm-2017/source/paper.tex
Revise intro to partial trust model.

\section{Trust}

@@

The well-known and widely-used {\em web of trust} model
\cite{zimmermann_official_1995,ferguson_practical_2003}
is a decentralized alternative.
In a web of trust,
individuals choose who they trust initially.
Trust is then extended to new individuals if they are vouched for by a
currently-trusted individual,
making it possible to extend their web of trust to a large
number of nodes.
However, the web of trust approach assumes that trust can be extended
transitively,
which is not generally true
\cite{christianson_why_1997}.
The web of trust model also fails to account for the structure
of the trust network:
trusted nodes are all trusted equally,
regardless of how many nodes trust them.
Similarly, while the process of building a web of trust is decentralized,
the emergent structure of the trust network itself can be centralized.
In order to analyze the influence of network structure on adversarial
fault tolerance,
a different trust model is needed.

@@

@@

\section{Multipath Fault Tolerance}

>>>>

\section{Trust and Fault Tolerance}

@@

The well-known and widely-used {\em web of trust} model
\cite{zimmermann_official_1995,ferguson_practical_2003}
is a decentralized alternative.
In a web of trust,
individuals choose who they trust initially.
Trust is then extended to new individuals if they are vouched for by a
currently-trusted individual,
making it possible to extend their web of trust to a large
number of nodes.
However, the web of trust approach assumes that trust can be extended
transitively,
which is not generally true
\cite{christianson_why_1997}.
The web of trust model also fails to account for the structure
of the trust network:
trusted nodes are all trusted equally,
regardless of how many nodes trust them.
Similarly, while the process of building a web of trust is decentralized,
the emergent structure of the trust network itself might be centralized.
In order to analyze the influence of network structure on adversarial
fault tolerance,
a different trust model is needed.

@@

We can allow for more realistic transitivity assumptions and incorporate
network structure into a trust model with one key insight:
even if no single path between sender and receiver is fully trusted,
multiple message copies can be sent along different paths and compared
by the receiver to detect and correct errors.
However, in the presence of an attacker, there is only benefit in sending an
additional message along a path if that path does not share untrusted,
single points of failure with any of the existing message paths
(otherwise, the adversary can compromise both messages
with the same effort required to compromise one of them).
The maximum number of such paths represents the effective redundancy that
can be utilized by any redundancy-based fault tolerance scheme.
We now propose a model for quantifying the effective redundancy of a network
as a function of its structure and the level of trust transitivity.
We will then use this model to evaluate a specific fault-tolerance scheme.

@@

\subsection{Multipath Fault Tolerance}
